\hspace{25cm}Debiased Calibration for Generalized Two-Phase Sampling

### 2024-07-30 final/jsm_poster_ov.tex
Updated JSM poster. I think that it looks good.

        $$
        \hat w_{i} = \argmin_{w} \sum_{i \in A} G(w_i)
        \suchthat \sum_{i \in A} w_{i} {\bf{x}}_i = 
        \sum_{i \in U} {\bf{z}}_i,
        \sum_{i \in A} w_i g(d_i) = \sum_{i \in U} g(d_i) .
        $$

@@

    Let ${\bf{z}}_i = ({\bf x}_i / q_i, g(d_{2i|1}))^T$, the proposed debiased
    calibration estimator is 
    \vspace{-1.0cm}

@@

    where 
    \vspace{-0.5cm}

    \begin{equation}\label{eq:wmin}
    \hat w_{2i|1} = \argmin_{w_{2|1}} \sum_{i \in A_2} w_{1i} G(w_{2i|1}) q_i
    \suchthat \sum_{i \in A_2} d_{1i} w_{2i|1} {\bf{z}}_i q_i = 
    \sum_{i \in A_1} d_{1i} {\bf{z}}_i q_i.
    \end{equation}

@@

    $$\hat Y_{\ell}(\bm \lambda^*, \bm \phi^*) = \hat Y_{\rm{DEE}}+ 
    \left(\sum_{i \in A_1} d_{1i} {\bf z}_i q_i - \sum_{i \in A_2} d_{1i} 
    \pi_{2i \mid 1}^{-1}  {\bf z}_i q_i\right)\bm \phi^*$$

@@

    $$
    \bm \phi^* = 
    \left[\sum_{i \in U} \frac{\pi_{2i|1}{\bf z}_i {\bf z}_i^T q_i}{g'(d_{2i|1})}\right]^{-1}
    \sum_{i \in U} \frac{\pi_{2i|1}{\bf z}_i y_i}{g'(d_{2i|1})}.
    $$

@@

    \item[4.] Debiased Calibration with Estimated Population Constraints (DC-Est):
      This solves Equation~\eqref{eq:wmin} with $q_i = 1$.
  \end{itemize}

>>>>

        $$
        \hat w_{i} = \argmin_{w} \sum_{i \in A} G(w_i)
        \suchthat \sum_{i \in A} w_{i} {\bf{x}}_i = 
        \sum_{i \in U} {\bf{x}}_i,
        \sum_{i \in A} w_i g(d_i) = \sum_{i \in U} g(d_i) .
        $$

@@

    Let ${\bf{z}}_i = ({\bf x}_i, g(d_{2i|1}))^T$, the proposed debiased
    calibration estimator is 
    \vspace{-1.0cm}

@@

    where $d_{1i} = \pi_{1i}^{-1}, d_{2i \mid 1}= \pi_{2i \mid 1}^{-1}$ and 
    \vspace{-0.5cm}

    \begin{equation}\label{eq:wmin}
    \hat w_{2i|1} = \argmin_{w_{2|1}} \sum_{i \in A_2} d_{1i} G(w_{2i|1})
    \suchthat \sum_{i \in A_2} d_{1i} w_{2i|1} {\bf{z}}_i = 
    \sum_{i \in A_1} d_{1i} {\bf{z}}_i.
    \end{equation}

@@

    $$\hat Y_{\ell}(\bm \lambda^*, \bm \phi^*) = \hat Y_{\rm{DEE}}+ 
    \left(\sum_{i \in A_1} d_{1i} {\bf z}_i - \sum_{i \in A_2} d_{1i} 
    \pi_{2i \mid 1}^{-1}  {\bf z}_i \right)\bm \phi^*$$

@@

    $$
    \bm \phi^* = 
    \left[\sum_{i \in U} \frac{\pi_{2i|1}{\bf z}_i {\bf z}_i^T}{g'(d_{2i|1})}\right]^{-1}
    \sum_{i \in U} \frac{\pi_{2i|1}{\bf z}_i y_i}{g'(d_{2i|1})}.
    $$

@@

    \item[4.] Debiased Calibration with Estimated Population Constraints (DC-Est):
      This solves Equation~\eqref{eq:wmin}.
  \end{itemize}
